---
title: "Assignment 1"
---

------------------------------------------------------------------------

------------------------------------------------------------------------

# Assignment 1

My first assignment has two parts.

## (a) 

Summary:

Mustafa Gokce Baydogan, the founder of Algopoly and an industrial engineer, shared his career experiences and emphasized the importance of data science, modeling, and optimization in his company. He highlighted the need to analyze data before building models, mentioning projects like shoe sales forecasting and wood warping during the drying process. In these projects, he used image data and applied linear regression to achieve higher-quality products. He also discussed the challenges of balancing supply and demand in the electricity market, the recommendation algorithms at Trendyol, and how machine learning can be applied to optimization.

1.According to Mustafa Gokce Baydogan, how does machine learning contribute to optimization processes?

A\) By visualizing data.

B\) By having the potential to improve optimization techniques.

C\) By enabling faster data collection.

D\) By directly reducing costs.

**answer:** B

In the wood warping project, what method did Baydogan use to achieve higher-quality products?

A\) Linear regression and image analysis.

B\) Clustering analysis.

C\) Neural networks.

D\) Time series analysis.

**answer:** A

## (b)

\# Load the necessary library and Import the polls_us_election_2016

```{r}
library(dslabs)
data(polls_us_election_2016)
```

\# Display the first 10 rows of the data

```{r}
head(polls_us_election_2016, 10)

```

\# Calculate the total number of missing values NA

```{r}
total_number_of_NA <- sum(is.na(polls_us_election_2016))
print(total_number_of_NA)
```

\# Define variables for my birth year and my first name, define a function to change missing values, apply the function to each column of the data to fill missing values, assign the changed data to a new variable, calculate the total number of missing values in the changed data, print the count of missing values in the modified data

```{r}
my_birth_year <- 2003
my_first_name <- "Elif"

change_na_values <- function(x) {
  if (is.numeric(x)) {
    return(ifelse(is.na(x), my_birth_year, x))  
  } else {
    return(ifelse(is.na(x), my_first_name, x))
  }
}

polls_us_election_2016 <- as.data.frame(lapply(polls_us_election_2016, change_na_values))

changed_data <- polls_us_election_2016

total_number_of_na_for_changed <- sum(is.na(changed_data))
print(total_number_of_na_for_changed)

```

\# Display the first 10 rows of the modified data

```{r}
head(changed_data, 10)
```
