---
title: "Assignment 1"
---

------------------------------------------------------------------------

------------------------------------------------------------------------

# Assignment 1

My first assignment has two parts.

## (a)

## (b)

\# Load the necessary library and Import the polls_us_election_2016

```{r}
library(dslabs)
data(polls_us_election_2016)
```

\# Display the first 10 rows of the data

```{r}
head(polls_us_election_2016, 10)

```

\# Calculate the total number of missing values NA

```{r}
total_number_of_NA <- sum(is.na(polls_us_election_2016))
print(total_number_of_NA)
```

\# Define variables for my birth year and my first name, define a function to change missing values, apply the function to each column of the data to fill missing values, assign the changed data to a new variable, calculate the total number of missing values in the changed data, print the count of missing values in the modified data

```{r}
my_birth_year <- 2003
my_first_name <- "Elif"

change_na_values <- function(x) {
  if (is.numeric(x)) {
    return(ifelse(is.na(x), my_birth_year, x))  
  } else {
    return(ifelse(is.na(x), my_first_name, x))
  }
}

polls_us_election_2016 <- as.data.frame(lapply(polls_us_election_2016, change_na_values))

changed_data <- polls_us_election_2016

total_number_of_na_for_changed <- sum(is.na(changed_data))
print(total_number_of_na_for_changed)

```

\# Display the first 10 rows of the modified data

```{r}
head(changed_data, 10)
```
